Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments

### 2019-03-08 Journal/JINT 2018/JINT18_rev1.tex
mostly done with reviewer response letter & edits

\begin{abstract}
This paper presents a stochastic framework for autonomous exploration and patrol with multiple cooperating robots. The first contribution extends the authors' prior work in single-robot exact occupancy grid mapping and autonomous exploration in a 2D environment to mapping and exploring in a 3D environment. The proposed 3D occupancy grid map is computed efficiently and is scalable to larger and more complex scenarios for real-time mapping. Important aspects of this 3D map are projected onto a 2D occupancy grid map, where an autonomous exploration algorithm is designed to select robotic motions that maximize map information gain. The mapping and exploration algorithms are demonstrated with an experiment where a quadrotor autonomously maps and explores an initially-uncertain environment. The second contribution is a novel approach to multi-vehicle cooperative patrol of environments based on map uncertainty. A cooperative autonomous exploration algorithm applies a bidding-based framework to coordinate robotic efforts for improving occupancy grid map information gain. Since these exploration approaches are based on probabilistic knowledge about the map, the 3D occupancy grid map is systematically degraded over time to encourage the robots to revisit regions as time passes, thereby patrolling the environment. Furthermore, using a Bayesian framework and receding horizons, the algorithm is robust to dynamic obstacles within the mapping space. The efficacy of the proposed multi-vehicle cooperative patrol is illustrated with a simulation involving three robots patrolling a large floor plan with a non-cooperative person walking around the space.
\keywords{Cooperative Patrol \and Multi-Vehicle Autonomous Exploration \and 3D Occupancy Grid Mapping}
\end{abstract}

@@

We propose an autonomous exploration strategy that selects motions that move the robot to poses that are expected to maximize information gain. The probabilistic map is used for acquiring entropy as a measure of uncertainty, and for collision avoidance. For these processes, careful consideration must be placed on computation. In particular, the computational complexity for expected entropy of a single measurement ray intersecting $n_r$ cells is $\mathcal O(n_r^2)$. To address this issue, we propose projecting the 3D map onto a 2D occupancy grid map, which is located at the desired height of exploration. This approach corresponds to vertically-uniform environments such as rooms and hallways without complex geometries. Projecting the occupancy grid map simplifies the exploration through 3D space, and decreases $n_r$, thereby increasing the algorithm speed.

@@

The proposed approach uses auctions and bid modifications based on total map expected information gain and collision-avoidance, promoting exploration of different spaces without explicit consideration of coverage overlaps. The pseudocode for the bidding process is shown with Algorithm \ref{alg:bidding}.

@@

>>>>

\begin{abstract}
This paper presents a stochastic framework for autonomous exploration and patrol with multiple cooperating robots. The first contribution extends the authors' prior work in single-robot exact occupancy grid mapping and autonomous exploration in a 2D environment to mapping and exploring in a 3D environment. The proposed 3D occupancy grid map is computed efficiently using an inverse sensor model that accounts for the sensor uncertainty, where we propose several measurement sources may be fused together by considering depth readings individually. This approach is scalable to larger and more complex scenarios for real-time mapping. Furthermore, this paper shows how important aspects of a 3D map representing a structured environment are projected onto a 2D occupancy grid map, where an autonomous exploration algorithm is designed to select robotic motions that maximize map information gain. The mapping and exploration algorithms are demonstrated with an experiment where a quadrotor autonomously maps and explores an initially-uncertain environment. The second contribution is a novel approach to multi-vehicle cooperative patrol of environments based on map uncertainty. We propose a cooperative autonomous exploration algorithm, which applies a bidding-based framework to coordinate robotic efforts for improving occupancy grid map information gain. Since these exploration approaches are based on probabilistic knowledge about the map, the 3D occupancy grid map is systematically degraded over time to encourage the robots to revisit regions as time passes, thereby patrolling the environment. Furthermore, using a Bayesian framework and receding horizons, the algorithm is robust to dynamic obstacles within the mapping space. The efficacy of the proposed multi-vehicle cooperative patrol is illustrated with a simulation involving three robots patrolling a large floor plan with a non-cooperative person walking around the space.
\keywords{Cooperative Patrol \and Multi-Vehicle Autonomous Exploration \and 3D Occupancy Grid Mapping}
\end{abstract}

@@

We propose an autonomous exploration strategy that selects motions that move the robot to poses that are expected to maximize information gain. The probabilistic map is used for acquiring entropy as a measure of uncertainty, and for collision avoidance. For these processes, careful consideration must be placed on computation. In particular, the computational complexity for expected entropy of a single measurement ray intersecting $n_r$ cells is $\mathcal O(n_r^2)$~\cite{KauAiLee16}. To address this issue, we propose projecting the 3D map onto a 2D occupancy grid map, which is located at the desired height of exploration. This approach corresponds to vertically-uniform environments such as rooms and hallways without complex geometries. Projecting the occupancy grid map simplifies the exploration through 3D space, and decreases $n_r$, thereby increasing the algorithm speed.

@@

The proposed approach uses auctions and bid modifications based on total map expected information gain and collision-avoidance, promoting exploration of different spaces without explicit consideration of coverage overlaps. For the vehicle that wins the first bid, it moves toward the candidate pose that maximizes its contribution to map information gain with travel cost. The subsequent auctions produce an optimal solution except for the actions of prior auction-winning robots, but these actions are explicitly considered. In this sense, we achieve a near-optimal coordinated solution without major computational bottlenecks. 
The pseudocode for the bidding process is shown with Algorithm \ref{alg:bidding}.

@@

The research presented in this paper may be enhanced in several ways. First, this research assumes fixed map limits. In practice, a robot may not be given knowledge of the environment size. A mapping and exploration algorithm that is capable of growing as it explores could increase the number of applications for such robots. Additionally, localization can be challenging in uncertain environments, can be included in the exploration policy.

### 2019-03-08 Journal/JINT 2018/JINT_ans.tex
mostly done with reviewer response letter & edits

%The focus of this paper is probabilistic mapping and autonomous exploration, not control system design for stabilization or tracking. In fact, the exploration algorithm serves to determine an optimal trajectory for the robot as it gathers knowledge about its environment, and as such, it deals with a guidance problem. Designing a specific control system to follow this trajectory may be achieved by a wide range of controllers, and it is out of scope of this paper. 
%
%To clarify this, the end of Section 5 is modified as follows. 
%
%\begin{correction}The starting and ending positions and attitudes may be constrained, and polynomials patched together for long trajectories share a common position and velocity with respect to time. Then, the robot tracks this trajectory until the robot falls within acceptable thresholds of the final optimal pose. For generality of the proposed exploration algorithm, any position controller yielding robotic motion that follows this desired trajectory may be selected. Once the robot completes this motion, the entire process is repeated.\end{correction}

\item {\itshape Reviewer \#2: A reference should be added to support the following sentence in Section 3.2: " In particular, the computational complexity for expected entropy of a single measurement ray intersecting $n_r$ cells is $\mathcal{O}(n_r^2)$''. The authors can alternatively show how the computational complexity was calculated.}

\item {\itshape Reviewer \#2: The following claim mentioned in the conclusion should be justified: "This paper introduces a near-optimal bidding-based solution to multi-vehicle exploration and patrol to map a 3D space". How did the authors conclude that their proposed solution is a near-optimal one?}

\item {\itshape Reviewer \#2: The authors should discuss the limitations and\/or disadvantages of the proposed framework in the conclusion section.}

@@

\item {\itshape Reviewer \#2: The authors may suggest some directions for future work based on the proposed framework.
}

>>>>

The abstract is revised to place more focus on the authors' contributions as follows.

\begin{correction}This paper presents a stochastic framework for autonomous exploration and patrol with multiple cooperating robots. The first contribution extends the authors' prior work in single-robot exact occupancy grid mapping and autonomous exploration in a 2D environment to mapping and exploring in a 3D environment. The proposed 3D occupancy grid map is computed efficiently using an inverse sensor model that accounts for the sensor uncertainty, where we propose several measurement sources may be fused together by considering depth readings individually. This approach is scalable to larger and more complex scenarios for real-time mapping. Furthermore, this paper shows how important aspects of a 3D map representing a structured environment are projected onto a 2D occupancy grid map, where an autonomous exploration algorithm is designed to select robotic motions that maximize map information gain. The mapping and exploration algorithms are demonstrated with an experiment where a quadrotor autonomously maps and explores an initially-uncertain environment. The second contribution is a novel approach to multi-vehicle cooperative patrol of environments based on map uncertainty. We propose a cooperative autonomous exploration algorithm, which applies a bidding-based framework to coordinate robotic efforts for improving occupancy grid map information gain. Since these exploration approaches are based on probabilistic knowledge about the map, the 3D occupancy grid map is systematically degraded over time to encourage the robots to revisit regions as time passes, thereby patrolling the environment. Furthermore, using a Bayesian framework and receding horizons, the algorithm is robust to dynamic obstacles within the mapping space. The efficacy of the proposed multi-vehicle cooperative patrol is illustrated with a simulation involving three robots patrolling a large floor plan with a non-cooperative person walking around the space.\end{correction}

\item {\itshape Reviewer \#2: A reference should be added to support the following sentence in Section 3.2: ``In particular, the computational complexity for expected entropy of a single measurement ray intersecting $n_r$ cells is $\mathcal{O}(n_r^2)$''. The authors can alternatively show how the computational complexity was calculated.}

This calculation is shown in reference [9], which now follows the statement in this paper.

\item {\itshape Reviewer \#2: The following claim mentioned in the conclusion should be justified: ``This paper introduces a near-optimal bidding-based solution to multi-vehicle exploration and patrol to map a 3D space''. How did the authors conclude that their proposed solution is a near-optimal one?}

The following is added to the end of Section 4.2 to justify this claim.

\begin{correction}For the vehicle that wins the first bid, it moves toward the candidate pose that maximizes its contribution to map information gain with travel cost. The subsequent auctions produce an optimal solution except for the actions of prior auction-winning robots, but these actions are explicitly considered. In this sense, we achieve a near-optimal coordinated solution without major computational bottlenecks.\end{correction}

\item {\itshape Reviewer \#2: The authors should discuss the limitations and/or disadvantages of the proposed framework in the conclusion section.
\\
The authors may suggest some directions for future work based on the proposed framework.
}

Some of the disadvantages, which motivate future work, relate to implementation challenges. The following is added to the conclusions.

\begin{correction}ADD\end{correction}

@@

Reference [9] and [11] are auto-generated this way because they have an identical author list.
